The Spatial Distribution of Local Group Satellites in a Cosmological Context

### 2016-06-14 paper/ms.tex
intro new paragraph

%\subsection{Evidencias observacionales de planos:}
\noindent Since the early works of (el que libeskind dice que habló de
eso primero) and Lynden-Bell (1976), the observed anisotropic
distribution of satellite galaxies in the Local Group has been a key
point in the discussion of galaxy formation models within $\Lambda$CDM
cosmology. These pioneer papers described that the then known satellite
galaxies of the Milky May (MW) were distributed roughly following the plane
that contained the Magelanic clouds and their stellar tails. This
anisotropic distribution was further studied in the work of Pawlowski
et. al. (2012), where they included all the known MW satellite galaxies (XXX
more than in the original Lynden-Bell paper) as well as some MW globular
clusters, and found that they are all contained in what they call a
"Vast Plane Of Satellites" (VPOS). This structure is around 30kpc thick and
is perpendicular to the stellar disc of the MW galaxy. This plane of
satellites was considered a rarity until the PAndAS survey of the
Andromeda (M31) galaxy and its halo (missing reference on the survey)
provided a complete sample of the satellite galaxy population (above a
XXXX magnitude) of our neighboring galaxy, allowing their consistent distance
estimations (Conn et al. 2012). In a groundbreaking work, Ibata et
al. (2013) found that 15 out of the 30 satellites are in a planar
structure that is 15kpc thick and has an extension of 400kpc.
Additionally, from line of sight velocity measurements, they
found that the structure has an apparent coherent rotation, with the
satellites south of M31 moving away from us and those north of M31
coming towards us. This apparent organized rotation of satellite galaxies was also
statistically found to occur in diametrically opposed 
pairs of satellites from the SDSS (Ibata et al. 2014), although this
results were contested in a follow up paper by Cuatun et al. (2014).

@@

These observed planes present a challenge for current galaxy formation
models (Pawlowski et al. 2014)

>>>>

%\subsection{Evidencias observacionales de planos:}
\noindent Since the early works of (el que libeskind dice que habló de
eso primero) and \cite{1976MNRAS.174..695L}, the observed anisotropic
distribution of satellite galaxies in the Local Group has been a key
point in the discussion of galaxy formation models within $\Lambda$CDM
cosmology. These pioneer papers described that the then known satellite
galaxies of the Milky May (MW) were distributed roughly following the plane
that contained the Magelanic clouds and their stellar tails. This
anisotropic distribution was further studied in the work of \cite{}Pawlowski
et. al. (2012), where they included all the known MW satellite galaxies (XXX
more than in the original Lynden-Bell paper) as well as some MW globular
clusters, and found that they are all contained in what they call a
"Vast Plane Of Satellites" (VPOS). This structure is around 30kpc thick and
is perpendicular to the stellar disc of the MW galaxy. This plane of
satellites was considered a rarity until the PAndAS survey of the
Andromeda (M31) galaxy and its halo (missing reference on the survey)
provided a complete sample of the satellite galaxy population (above a
XXXX magnitude) of our neighboring galaxy, allowing their consistent distance
estimations (Conn et al. 2012). In a groundbreaking work, Ibata et
al. (2013) found that 15 out of the 30 satellites are in a planar
structure that is 15kpc thick and has an extension of 400kpc.
Additionally, from line of sight velocity measurements, they
found that the structure has an apparent coherent rotation, with the
satellites south of M31 moving away from us and those north of M31
coming towards us. This apparent organized rotation of satellite galaxies was also
statistically found to occur in diametrically opposed 
pairs of satellites from the SDSS (Ibata et al. 2014), although this
results were contested in a follow up paper by Cuatun et al. (2014).

@@

These observed planes and their apparent co-rotation seem to challenge current galaxy formation models (Pawlowski et al. 2014). 
A few months after the discovery of the M31 plane of satellites, Bahl and Baumgardt (2013) looked for similar structures in the MilleniummII dark matter only cosmological simulations, and found that planar structures are common (they found them in around 2 per cent of host halos). 
Nevertheless these results were contradicted by the works of Ibata el al. (2014) and Pawlowski et al. (2014) who, analyzing the same cosmological simulations with methods closer to those used to analyze the observational data, found that planar structures such as that observed in M31 are extremely rare (less than 0.02 per cent or 0.004 per cent respectively).\\
